GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
fix typo
hoisting too far away

\subsection{Hoisting too far away}
\begin{enumerate}
\item When the hoist point is too far.
\item When the number of instructions we may cross is very high.
\end{enumerate}

>>>>

\subsection{Hoisting too far away}
When we load a value from memory, we require an extra register to keep the value
around. Hoisting a load means we need to keep the value alive for a longer
period. That could result in spills later in the register allocation.

Also, if there are several instructions in between the hoisting point and the
instruction to be hoisted, the instruction to be hoisted crosses several
instructions while hoisting, it means we are adding one register to all the
live-ranges spanning the instructions. That could result in spills.

\begin{enumerate}
\item When the hoist point is too far.
\item When the number of instructions we may cross is very high.
\end{enumerate}
